\documentclass{article}

\usepackage{booktabs}

\usepackage{fancyhdr}
\pagestyle{fancy}

\begin{document}

\lhead{\textbf{Team 6}:\\
	Jiahao, Li\\
	Pavithran, Pathmarajah\\
	Viren Patel }

\newpage

\title{Problem Statement}
\section*{\\\\Revision History}

\begin{table}[h!]
  \centering
  \caption{Revision History: Problem Statement}
  \label{tab:table1}
  \begin{tabular}{cccc}
	\toprule
	Date &  Developer & Change & Revision\\
	\midrule
	September 22&Jiahao Li &Initial Draft &0\\
	September 22&Pavithran Pathmarajah &Initial Draft &0\\
	September 22&Viren Patel  &Initial Draft &0\\
	\bottomrule
  \end{tabular}
\end{table}

\newpage

\section*{Problem Statement}

\subsection{What problem are you trying to solve?}
Video games are a means of entertainment used by all age groups, the trouble is for some of these groups the process of acquiring and running these games can be a hassle. We                                plan to contribute to solving this problem by reintroducing Tanks the game, but as animproved web based version. We are trying to make it more accessible to the entire user base as the                                     accessibility is currently hindered by the need to download and compile the game on their computer if they wish to play. By transferring Tanks to the web, we are making sure that the                                     users are not restricted by the platform they are using. We are also eliminating the process of downloading and compiling, making it more convenient for all users. 

\subsection{Why is this an important problem?}
Now that the original game, FlappyBird, is no longer available on the mobile device application market, we've created a way for people to play it once again. FlappyBird was an extremely popular game that was removed from the application market by its original developer and it received millions of downloads and reviews daily at its prime. However, after its removal, many people were unable to share their high scores with other people. By recreating a free web application that allows multiple users to play this game, we've allowed for people to dive into the fun and entertainment that FlappyBird provides once again.

\subsection{What is the context of the problem you are solving?}
Our recreation of FlappyBird is a game that can be played by all ages and is not limiting in its platforms. Almost every device is able to access a web browser and run JavaScript. This creates an environment for users to play the game for free and without any downloads allowing for a more accessible way to play this game than previously available.

\end{document}